---
title: "Getting_Started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting_Started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(spatialEpisim.foundation)
```

# Installation
Installation is covered in the [Installation](TODO) vignette.

# Storage configuration
Unless the [spatialEpisim.data] package (included in the list of suggested
packages in the DESCRIPTION file of this package) is installed and successfully
attached, then the option `spatialEpisim.foundation.datapath` must be set
correctly.

The path described in the option `spatialEpisim.foundation.datapath` is used for
storing spatial raster and vector data that is needed for
spatialEpisim.foundation to be useful.

By default, if this option is `NULL` is set to
`path.expand("~/spatialEpisim.foundation.data")`.

# Setup for simulation
[SVEIRD.BayesianDataAssimilation] is used with an object referred to as
`layers`. This SpatRaster-classed object contains layers for each of the
compartments in an SVEIRD simulation.

<!-- TODO: open an issue to track SVEIRD, SEIRD, SEIR, et cetera simulations.
These sorts of simulations cannot be run yet (all simulations are SVEIRD), and
therefore the `layers` object must have layers for each of the compartments.
When other compartmental models are possible the shape of `layers` must be
decided upon. -->

# Raster aggregation
[getSVEIRD.SpatRaster] is the function used to aggregate a SpatRaster, and it
will call [maskAndClassifySusceptibleSpatRaster] for the user, masking it with
the provided SpatVector object. This is the easiest way to aggregate a
SpatRaster object for use with spatialEpisim.foundation. Aggregation without
this function, *id est* using `terra::aggregate` on a SpatRaster beforehand,
will lead to inaccurate results, because the `aggregationFactor` argument of
[getSVEIRD.SpatRaster] and [SVEIRD.BayesianDataAssimilation] is used throughout
various parts of the algorithm.

If this approach to aggregation does not meet your needs, please contact the
maintainer of the package and request a feature enhancement that meeds your
needs, or fork the project and modify it to your needs.

It's recommended to define a variable, `rasterAggregationFactor`, to pass to
both [SVEIRD.BayesianDataAssimilation] and [getSVEIRD.SpatRaster] to ensure it
is the same. See the examples for the former function.

# Preparing seed data
Seed data is required in a wide format; see the [initialInfections.fourCities]
data description for its shape. The Location variable is the names of cities,
which should be found within the names of the SpatVector provided to
[getSVEIRD.SpatRaster].
